An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-10-01 gas-adsorption/gas-ads-revtex.tex
comment out comments to referees

\startreferees{Explain how the point of our paper is not to find structure-property relationships.}
Several studies elucidated relationships between structural features of nanoporous materials---such as void fraction, pore size, and surface area---and their deliverable capacity of various gases \cite{gomez2014exploring,ahmed2019exceptional,simon2015materials,moghadam2018computer,Tong2018}. 
Such structure-property relationships serve as useful heuristics for designing new materials with high deliverable capacity. However, the intention of our paper is not to discover structure-property relationships. 
Rather, we place our upper bound on the deliverable capacity of [rigid] materials that holds irrespective of how the structural features of the material are tuned.

\donereferees

\startreferees{Discuss gravimetric vs volumetric deliverable capacity}

@@

\donereferees

>>>>

% \startreferees{Explain how the point of our paper is not to find structure-property relationships.}
Several studies elucidated relationships between structural features of
nanoporous materials---such as void fraction, pore size, and surface area---and
their deliverable capacity of various gases
\cite{gomez2014exploring,ahmed2019exceptional,simon2015materials,moghadam2018computer,Tong2018}.
Such structure-property relationships serve as useful heuristics for designing
new materials with high deliverable capacity. However, the intention of our
paper is not to discover structure-property relationships. Rather, we place our
upper bound on the deliverable capacity of [rigid] materials that holds
irrespective of how the structural features of the material are tuned.

% \donereferees

% \startreferees{Discuss gravimetric vs volumetric deliverable capacity}

@@

% \donereferees
